Red Wine Quality Exploration by Karina Lund
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(gridExtra)
library(GGally)
library(scales)
library(memisc)
library(psych)

```

```{r echo=FALSE, Load_the_Data}

# Load the Data
redwine <- read.csv('wineQualityReds.csv', header = T)

```

This data set contains 1,599 red wines with 11 variables on the
chemical properties of the wine. At least 3 wine experts rated the quality of
each wine, providing a rating between 0 (very bad) and 10 (very excellent).
"Which chemical properties influence the quality of red wines?" is the question I will try to find answer to.

# Univariate Plots Section

> **Tip**: In this section, you should perform some preliminary exploration of
your dataset. Run some summaries of the data and create univariate plots to
understand the structure of the individual variables in your dataset. Don't
forget to add a comment after each plot or closely-related group of plots!
There should be multiple code chunks and text sections; the first one below is
just to help you get started.

First 10 rows from dataset
```{r echo=FALSE, Univariate_Plots}

head(redwine, 10)

```

Dimensions of the dataset 
```{r echo=FALSE}

dim(redwine)

```

Dataset stucture
```{r echo=FALSE}

str(redwine)

```

Dataset summary
```{r echo=FALSE}

summary(redwine)

```

```{r echo=FALSE}

p1 <- ggplot(aes(x=fixed.acidity), data=redwine) + 
  geom_histogram(binwidth=0.3, color = I('black'), fill=  I('#673147'))
p2 <- ggplot(aes(x=volatile.acidity), data=redwine) + 
  geom_histogram(bins = 150, color = I('black'), fill = I('white'))
p3 <- ggplot(aes(x=citric.acid), data=redwine) + 
  geom_histogram(bins = 150, color = I('black'), fill=  I('#FFF44F'))
grid.arrange(p1, p2, p3, ncol = 1)

```

The principal organic acids found in grapes are tartaric, malic; to a small 
extent, citric and others Tartaric acid (fixed acidity) and malic acid account 
for over 90% of the total acids present. Fixed acidity in dataset has a range 
from 4.6 to 15.90 g/dm^3, while volatile and citric acids have a range from 0.12
to 1.5 and 0 to 1 respectively. Volatile acidity is responsible for the sour
taste of vinegar. An excessive amount of acetic acid is also considered a wine
fault. Citric acid increases acidity and gives a "fresh" flavor. There are over
150 wines that doesn't conatin citric acid at all. That is a normal situastion
because many types of red wines do not contain any citric acid.

```{r echo=FALSE}

p1 <- ggplot(aes(x=free.sulfur.dioxide), data=redwine) + geom_histogram(bins = 60,  color = I('black'), fill = I('white'))
p2 <- ggplot(aes(x=total.sulfur.dioxide), data=redwine) + geom_histogram(bins = 60,  color = I('black'), fill = I('white'))
grid.arrange(p1, p2, ncol = 1)

```
 
Sulfur dioxide serves as an antibiotic and antioxidant, protecting wine from
spoilage by bacteria and oxidation. Its antimicrobial action also helps to 
minimize volatile acidity. Nose will be able to detect SO2 in wine in the range
of 15-40 ppm or higher dosage. If wine contains too much sulphurs, person can be able to taste it and that's nasty taste. 

There is no wine in dataset that are totally free for sulfur dioxide. Naturally
occurring sulfites are generated in very small amounts ranging from 6 to 40 ppm.
Most of wines in collection have a free sulfur dioxide under 21 mg / dm^3 and a
total sulfur dioxide under 62 mg / dm^3. There are two wines that have a very
hign total suflur dixide compared to others.

```{r echo=FALSE}

p1 <- ggplot(aes(x=residual.sugar), data=redwine) + 
        geom_histogram(binwidth=0.5, color= I('black'), fill = I('#7F1734'))
p2 <- ggplot(aes(x=residual.sugar), data=redwine) + 
        geom_histogram(bins = 30,color= I('black'), fill = I('#7F1734')) +
        scale_x_log10()
p3 <- ggplot(aes(x=chlorides), data=redwine) + 
        geom_histogram(bins = 30, color= I('black'), fill = I('#7F1734'))
p4 <- ggplot(aes(x=chlorides), data=redwine) +
        geom_histogram(binwidth=0.05, color= I('black'), fill = I('#7F1734')) +
        scale_x_log10()
p5 <- ggplot(aes(x=sulphates), data=redwine) + 
        geom_histogram(bins = 30, color= I('black'), fill = I('#7F1734'))
p6 <- ggplot(aes(x=sulphates), data=redwine) + 
        geom_histogram(bins = 30, color= I('black'), fill = I('#7F1734')) +
        scale_x_log10()
grid.arrange(p1, p2, p3, p4, p5, p6, ncol = 2)

```

Residual Sugar is the level of glucose and fructose (grape sugars) that are not converted into alcohol during fermentation.
Sodium chloride shows amount of salt in the wine.
Potassium sulphate is a "wine stabilizer". It has a bitter, salty taste. 
Residual Sugar, chlorides and sulphates are right skewed, that's why log10 transformation is used.


```{r echo=FALSE, fig.width=7, fig.height=7}

p1 <- ggplot(aes(x=alcohol), data=redwine) + 
        geom_histogram(binwidth=0.25, color= I('black'), fill = I('#7F1734'))
p2 <- ggplot(aes(x=density), data=redwine) + 
        geom_histogram(bins = 30, color= I('black'), fill = I('#7F1734'))
p3 <- ggplot(aes(x=pH), data=redwine) +
        geom_histogram(binwidth=0.05, color= I('black'), fill = I('#7F1734'))
grid.arrange(p1, p2, p3, ncol = 1)

```
Alcohol directly correlates to the ripeness (sugar content) of grapes. As grapes
ferment, the sugar converts to alcohol.

Density in wine is generally used as a measure of the conversion of sugar to
alcohol.

Winemakers use pH as a way to measure ripeness in relation to acidity. Low pH
wines will taste tart and crisp, while higher pH wines are more susceptible to
bacterial growth. Most wine pH's fall around 3 or 4. pH from 3.3 to 3.6 is best
for red wines. Most wines in dataset has pH from 3.2 to 3.4.

Density and pH are distributed normally.

```{r echo=FALSE}
ggplot(aes(x=quality), data=redwine) + 
  scale_x_continuous(limits = c(0, 10), breaks = seq(1, 10, 1)) +
  geom_histogram(binwidth=0.5, fill = I('#7F1734'))
```

There is no wine, that have got worst or best scores. Most of tested wines have
been rated by experts as average.

# Univariate Analysis

### What is the structure of your dataset?
Dataset contains 1599 red wines with 11 variables on the chemical properties of
the wine, such as fixed acidity, volatile acidity, citric acid, residual sugar,
sodium chloride,  free and total sulfur dioxides, density, pH, sulphates and alcohol.
Dataset also includes a quality rating of wine provided by experts.
Dataset doesn't contain any missing values. All columns are numerical.

### What is/are the main feature(s) of interest in your dataset?
I would like to determine which properties influence the quality of red wines most.
The main features of interest is quality.

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?
I can assume that acidity, alcohol and sugar influence the quality of red wine.
Volatile acidity is responsible for the sour taste of vinegar.
Citric acid gives a "fresh" flavor.
Sugar gives sweetnees.
It also could be sulfur dioxide, because high level of it can be detected by nose.
Or sulphate, because of bitter, salty taste.

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

Fixed and volatile acidity plots are right skewed, with some outliers with high amount of acids.
Citric acid histogram have 3 peaks: 0, 0.25 and 0.5 g/dm^3. Peak with 0 g/dm^3 if citric acid are highest. That can be explain  by a fact that some wines doesn't contain any citric acid at all.

Free and total sulful dioxide plots are right skrewed too. Free sulfur dioxide distribution have some outliers for values from 66-72. And Total sulfur dioxde have 2 outliers for value near 300 mg/dm^3.

Residual Sugar, chlorides and sulphates plots are right skewed and were log-transformed.
Distribution of pH and density is normal.
Since data is clean and does not contain any NA valus, I have not done any operation on data.

# Bivariate Plots Section

> **Tip**: Based on what you saw in the univariate plots, what relationships
between variables might be interesting to look at in this section? Don't limit
yourself to relationships between a main output feature and one of the
supporting variables. Try to look at relationships between supporting variables
as well.

```{r echo=FALSE, Bivariate_Plots, fig.height= 8, fig.width=8}
#ggpairs(redwine, columns = 2:13)
pairs.panels(redwine[2:13]) 
#[c(3,4,5,8,12,13)]

```

# Bivariate Analysis

> **Tip**: As before, summarize what you found in your bivariate explorations
here. Use the questions below to guide your discussion.

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

### What was the strongest relationship you found?


# Multivariate Plots Section

> **Tip**: Now it's time to put everything together. Based on what you found in
the bivariate plots section, create a few multivariate plots to investigate
more complex interactions between variables. Make sure that the plots that you
create here are justified by the plots you explored in the previous section. If
you plan on creating any mathematical models, this is the section where you
will do that.

```{r echo=FALSE, Multivariate_Plots}

```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

### Were there any interesting or surprising interactions between features?

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

# Final Plots and Summary

> **Tip**: You've done a lot of exploration and have built up an understanding
of the structure of and relationships between the variables in your dataset.
Here, you will select three plots from all of your previous exploration to
present here as a summary of some of your most interesting findings. Make sure
that you have refined your selected plots for good titling, axis labels (with
units), and good aesthetic choices (e.g. color, transparency). After each plot,
make sure you justify why you chose each plot by describing what it shows.

### Plot One
```{r echo=FALSE, Plot_One}

```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}

```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```

### Description Three

------

# Reflection

> **Tip**: Here's the final step! Reflect on the exploration you performed and
the insights you found. What were some of the struggles that you went through?
What went well? What was surprising? Make sure you include an insight into
future work that could be done with the dataset.

> **Tip**: Don't forget to remove this, and the other **Tip** sections before
saving your final work and knitting the final report!