Red Wine Quality Exploration by Karina Lund
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}

library(ggplot2)
library(gridExtra)
library(GGally)
library(scales)
library(memisc)
library(psych)

histogram_chart <- function(xaxis, 
                            xlabel, 
                            fillcolor, 
                            bincount = 60, 
                            scale10 = FALSE) {
    if (!scale10) {
      ggplot(aes(x = xaxis), data = redwine) + 
        geom_histogram(bins = bincount, color = I('black'), fill = I(fillcolor)) +
        xlab(xlabel)
    } else {
      ggplot(aes(x = xaxis), data = redwine) + 
        geom_histogram(bins = bincount, color = I('black'), fill = I(fillcolor)) +
        xlab(xlabel) +
        scale_x_log10()
    }
}

quality_box_chart <- function(xaxis, 
                              xlabel) {   
  ggplot(redwine, aes(quality, xaxis)) +
    geom_boxplot(aes(group = quality), outlier.alpha = 0.25) +
    ylab(xlabel) +
    scale_x_continuous(breaks = seq(3, 8, 1)) +
    coord_flip()
}

scatterplot_chart <- function(xaxis, 
                              yaxis, 
                              xlabel, 
                              ylabel, 
                              title = '') {
  ggplot(aes(x=xaxis, y = yaxis), data = redwine) + 
    geom_point(alpha = 0.3) +
    stat_smooth(method = 'lm') +
    xlab(xlabel) +
    ylab(ylabel) + 
    ggtitle(title)
}

color_chart <- function(xaxis, 
                        yaxis, 
                        xlabel, 
                        ylabel, 
                        title = '') {
  ggplot(redwine, aes(x = xaxis , y = yaxis, color = rating)) +
    geom_jitter(alpha = 0.7, size = 2) +
    scale_color_brewer(type='div', palette='RdYlGn') +
    xlab(xlabel) +
    ylab(ylabel) +
    ggtitle(title)
}

```

```{r echo=FALSE, Load_the_Data}

redwine <- read.csv('wineQualityReds.csv', header = T)

```

Dataset I analyzed contains 1,599 red wines with 11 variables of the chemical
properties of the wine. At least 3 wine experts rated the quality of each wine,
providing a rating between 0 (very bad) and 10 (excellent). 

"Which chemical properties influence the quality of red wines?" is the question
I will try to find answer to.

# Univariate Plots Section

First 10 rows from dataset
```{r echo=FALSE, Univariate_Plots}

head(redwine, 10)

```

Dimensions of the dataset 
```{r echo=FALSE}

dim(redwine)

```

Dataset structure
```{r echo=FALSE}

str(redwine)

```

Dataset summary
```{r echo=FALSE}

summary(redwine)

```

##Univariate plots

###Acids
```{r echo=FALSE, fig.height=8, fig.width=7.25}

p1 <- histogram_chart(redwine$fixed.acidity,
                      'fixed acidity', 
                      '#673147')
p2 <- histogram_chart(redwine$volatile.acidity,
                      'volatile acidity', 
                      'white')
p3 <- histogram_chart(redwine$citric.acid,
                      'citric acid', 
                      '#FFF44F')
grid.arrange(p1, p2, p3, 
             ncol = 1, 
             top = "Acids histogram")

```

The principal organic acids found in grapes are tartaric and malic, to a small 
extent, citric and others. Tartaric acid (fixed acidity) and malic acid account 
for over 90% of the total acids present.

Fixed acidity in dataset has a range from 4.6 to 15.90 g/dm³, while volatile 
and citric acids have a range from 0.12 to 1.5 and 0 to 1 respectively.

Volatile acidity is responsible for the sour taste of vinegar. An excessive
amount of acetic acid is also considered a wine fault.

Citric acid increases acidity and gives a "fresh" flavor. There are over 150
wines that doesn't contain citric acid at all. That is a normal situation
because many types of red wines do not contain any citric acid.


###Sulfur dioxide
```{r echo=FALSE}

p1 <- histogram_chart(redwine$free.sulfur.dioxide,
                      'free sulfur dioxide', 
                      'white')
p2 <- histogram_chart(redwine$total.sulfur.dioxide,
                      'total sulfur dioxide', 
                      'white')  
grid.arrange(p1, p2, 
             ncol = 1, 
             top = "Sulfur dioxides histogram")

```
 
Sulfur dioxide serves as an antibiotic and antioxidant, protecting wine from 
spoilage by bacteria and oxidation. Its antimicrobial action also helps to 
minimize volatile acidity. The nose will be able to detect SO2 in wine in the range 
of 15-40 ppm or higher dosage. If wine contains too much sulphur, person can be
able to taste it and that's nasty taste.

There is no wine in dataset that are totally free for sulfur dioxide. Naturally
occurring sulfites are generated in very small amounts ranging from 6 to 40 ppm.
Most of wines in collection have a free sulfur dioxide under 21 mg/dm³ and a
total sulfur dioxide under 62 mg/dm³. There are two wines that have a very
high total sulfur dioxide compared to others.

Total SO2 = Free SO2 + Bound SO2.  
If the wine is bottle-aged, the SO2 will decrease as more sulfites react with
other chemical constituents (sugars, acetaldehyde or phenolic compounds) in the
wine and become bound. Bound sulfur dioxide can be 50 - 90% of the amount of SO2
added to wine. I will create a new variable for bound SO2.

```{r echo=FALSE}

redwine$bound.sulfur.dioxide <- redwine$total.sulfur.dioxide - redwine$free.sulfur.dioxide

```

###Sugar, chlorides, sulphates
```{r echo=FALSE, fig.height=6, fig.width=7.25}

p1 <- histogram_chart(redwine$residual.sugar,
                      'residual sugar', 
                      '#7F1734', 
                      30)
p2 <- histogram_chart(redwine$residual.sugar,
                      'residual sugar', 
                      '#7F1734', 
                      30, 
                      TRUE)
p3 <- histogram_chart(redwine$chlorides,
                      'chlorides', 
                      '#7F1734', 
                      30)
p4 <- histogram_chart(redwine$chlorides,
                      'chlorides', 
                      '#7F1734', 
                      30, 
                      TRUE)
p5 <- histogram_chart(redwine$sulphates,
                      'sulphates', 
                      '#7F1734', 
                      30)
p6 <- histogram_chart(redwine$sulphates,
                      'sulphates', 
                      '#7F1734', 
                      30, 
                      TRUE)
grid.arrange(p1, p2, p3, p4, p5, p6, 
             ncol = 2,  
             top = "Sugar, chlorides, sulphates histograms")

```

Residual Sugar is the level of glucose and fructose (grape sugars) that are not
converted into alcohol during fermentation.

Sodium chloride shows amount of salt in the wine.

Potassium sulphate is a "wine stabilizer". It has a bitter, salty taste.

Residual Sugar, chlorides and sulphates are right skewed, that's why log10
transformation is used.


###Alcohol, density and pH

```{r echo=FALSE, fig.width=7, fig.height=7}

p1 <- histogram_chart(redwine$alcohol,
                      'alcohol', 
                      '#7F1734', 
                      30)
p2 <- histogram_chart(redwine$density,
                      'density', 
                      '#7F1734', 
                      30)
p3 <- histogram_chart(redwine$pH,
                      'pH', 
                      '#7F1734', 
                      30)
grid.arrange(p1, p2, p3, 
             ncol = 1, 
             top = "Alcohol, density and pH histograms")

```

Alcohol directly correlates to the ripeness (sugar content) of grapes. As grapes
ferment, the sugar converts to alcohol.

Density in wine is generally used as a measure of the conversion of sugar to 
alcohol.

Winemakers use pH as a way to measure ripeness in relation to acidity. Low pH 
wines will taste tart and crisp, while higher pH wines are more susceptible to 
bacterial growth. Most wine pH's fall around 3 or 4. pH from 3.3 to 3.6 is best 
for red wines. Most wines in dataset has pH from 3.2 to 3.4.

Density and pH are distributed normally.


###Quality
```{r echo=FALSE}

ggplot(aes(x=quality), data=redwine) + 
  scale_x_continuous(limits = c(0, 10), breaks = seq(1, 10, 1)) +
  geom_histogram(binwidth=0.5, fill = I('#7F1734')) + 
  ggtitle('Quality histogram')

```

There is no wine, that have got worst or best scores. Most of tested wines have
been rated by experts as average.
I will create a new variable rating by cutting quality in groups of 2.

```{r}

redwine$rating<- cut(redwine$quality, breaks = c(0,2,4,6,8,10))

```


# Univariate Analysis

### What is the structure of your dataset?
Dataset contains 1599 red wines with 11 variables on the chemical properties of 
the wine, such as fixed acidity, volatile acidity, citric acid, residual sugar, 
sodium chloride,  free and total sulfur dioxides, density, pH, sulphates and
alcohol. Dataset also includes a quality rating of wine provided by experts. 
Dataset doesn't contain any missing values. All columns are numerical.

### What is/are the main feature(s) of interest in your dataset?
I would like to determine which properties influence the quality of red wines
most. The main feature of interest is quality.

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?
I can assume that acidity, alcohol and sugar influence the quality of red wine. 
Volatile acidity is responsible for the sour taste of vinegar. Citric acid gives
a "fresh" flavor. Sugar gives sweetness. It also could be sulfur dioxide,
because high level of it can be detected by nose. Or sulphate, because of
bitter, salty taste.

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

I created 2 new variables:  
* bound SO2, which is difference between Total and Free SO2;  
* rating: for break quality in groups of 2.

Fixed and volatile acidity plots are right skewed, with some outliers with high 
amount of acids. Citric acid histogram has 3 peaks: 0, 0.25 and 0.5 g/dm³. Peak
with 0 g/dm³ if citric acid is highest. That can be explain  by a fact that
some wines don't contain any citric acid at all.

Free and total sulfur dioxide plots are right skewed too. Free sulfur dioxide 
distribution has some outliers for values from 66-72. And Total sulfur dioxide 
have 2 outliers for value near 300 mg/dm³.

Residual Sugar, chlorides and sulphates plots are right skewed and were 
log-transformed. Distribution of pH and density is normal. Since data is clean 
and does not contain any NA values, I have not done any operation on data.

# Bivariate Plots Section

Let's see how variables are correlated between each other.

```{r echo=FALSE, Bivariate_Plots, fig.height= 8, fig.width=8}

pairs.panels(redwine[2:13]) 

```

Strongest linear correlations:  
Fixed acidity: great positive correlation with citric acid, density and negative
correlation with pH  
Volatile acidity: quite negative correlation with citric acid  
Citric acid: quite negative correlation with pH  
Free sulfur dioxide: great positive correlation with total sulfur dioxide  
Alcohol: some positive correlation with quality.

### Exploring quality with other variables
```{r echo=FALSE, Bivariate_Plots_Details, fig.height= 9, fig.width=9}

p1 <- quality_box_chart(redwine$fixed.acidity, 
                        'fixed acidity')
p2 <- quality_box_chart(redwine$citric.acid, 
                        'citric acid')
p3 <- quality_box_chart(redwine$volatile.acidity, 
                        'volatile acidity')
p4 <- quality_box_chart(redwine$alcohol, 
                        'alcohol')
p5 <- quality_box_chart(log10(redwine$residual.sugar), 
                        'log10(residual sugar)')
p6 <- quality_box_chart(log10(redwine$total.sulfur.dioxide), 
                        'log10(total sulfur dioxide)')
p7 <- quality_box_chart(redwine$sulphates, 
                        'sulphates')
p8 <- quality_box_chart(redwine$pH, 
                        'pH')
p9 <- quality_box_chart(redwine$density, 
                        'density')
p10 <- quality_box_chart(redwine$chlorides, 
                         'chlorides')

grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, 
             ncol = 3, 
             top = 'Quality and wine attributes')
```

None of characteristics of wine doesn't have strong influence on quality of
wine. It was a surprise for me, I really thought that some of variables will
affect quality a lot.

Looking at pair plot and boxplots, we see that quality is positively correlated
with fixed and citric acids, sugar, sulphates and alcohol and negatively
correlated with volatile acidity, chlorides, sulfur dioxide, density and pH. 
Variables that affects quality of wine the most:  
1. Alcohol  
2. Volatile acidity  
3. Sulphates  
4. Citric acid  

After exploring boxplots, I can single out some trends for good wine quality:  
* more alcohol  
* less volatile acidity  
* more citric acid  
* more sulphates  
* less pH  
* less chlorides  
* density of best wines have lower median than other wine qualities  
* Residual sugar does not seems affect quality of the wines.  


###Relationship between other variables

There are some rules regarding wine components, which I would like to check:

  
#### pH and acidity

"lower the pH, the higher the total acidity in the wine""
```{r echo=FALSE}

scatterplot_chart(redwine$pH, 
                  redwine$fixed.acidity+redwine$citric.acid+redwine$volatile.acidity, 
                  'pH', 
                  'Total acidity', 
                  'pH and total acidity')

```

There are more than just 3 acids in wine, but here I used acids I have in
dataset. Scatterplot shows that some of acids and pH has a visible negative
correlation. Pearson correlation coefficient is -0.68, which indicates a near
strong relation.

```{r echo=FALSE}

cor.test(redwine$pH, 
         redwine$fixed.acidity+redwine$citric.acid+redwine$volatile.acidity, 
         method = 'pearson')$estimate

```

But there is something interesting, fixed acidity and citric acid have negative
correlation coefficients: -0.68 and -0.54, but volatile acidity has positive
0.23. It's a weak correlation, but it should be negative.

  
#### Alcohol and density

Alcohol level can be measured with wine hydrometer, which measure density. 
Since density of ethanol is 0.7893 g/cm³, which is lower than water, more alcohol
will cured to lower density. That's why I expect negative relationship between
these two variables.

```{r echo=FALSE}

scatterplot_chart(redwine$alcohol, 
                  redwine$density, 
                  'alcohol', 
                  'density', 
                  'alcohol and density')

```

Conclusion I make here is that higher alcohol concentration gives more dense.

  
#### Acids and density

Let's see relationship between acids and density. 
Density of acids, found in dataset are:  
* Tartaric acid: 1.79 g/cm³  
* Acetic acid: 1.05 g/cm³  
* Citric acid: 1.66 g/cm³ 

I expect that there will be a positive correlation between all 3 acids and
density and that tartaric acid and citric acid will have higher correlations than
acetic. Since density of citric acetic acid are almost equals 1 (density of the
water).

```{r echo=FALSE}
p1<-scatterplot_chart(redwine$density, 
                  redwine$fixed.acidity, 
                  'density', 
                  'fixed acidity')
p2<-scatterplot_chart(redwine$density, 
                  redwine$volatile.acidity, 
                  'density', 
                  'volatile acidity')
p3<-scatterplot_chart(redwine$density, 
                  redwine$citric.acid, 
                  'density', 
                  'citric acid')
grid.arrange(p1, p2, p3, ncol = 3, top = 'Density and wine acids')
```

This correlation is weaker than correlation between acids and pH, but
scatterplot still shows negative trend.

There are other strong correlations from pair plots.  
  
#### Sulfur dioxides

Total sulfur dioxide is a sum of free SO2 and bound SO2.

I want also to look at bound SO2 and see how it correlated to free SO2 and total
SO2. If the wine is bottle-aged, the SO2 will decrease as more sulfites react
with other chemical constituents (sugars, acetaldehyde or phenolic compounds) in
the wine and become bound. Bound sulfur dioxide can be 50 - 90% of the amount of
SO2 added to wine.

```{r echo = FALSE}

pairs.panels(redwine[c(7,8, 14)])

```
```{r echo=FALSE}
p1 <- scatterplot_chart(redwine$free.sulfur.dioxide, 
                  redwine$total.sulfur.dioxide, 
                  'free sulfur dioxide', 
                  'total sulfur dioxide')
p2 <- scatterplot_chart(redwine$bound.sulfur.dioxide, 
                  redwine$total.sulfur.dioxide, 
                  'bound sulfur dioxide', 
                  'total sulfur dioxide')
p3 <- scatterplot_chart(redwine$free.sulfur.dioxide, 
                  redwine$bound.sulfur.dioxide, 
                  'free sulfur dioxidee', 
                  'bound sulfur dioxide')
grid.arrange(p1, p2, p3, 
             ncol = 3, 
             top = 'Free, Bound and Total SO2')
```


Since both free and bound SO2 are parts of Total SO2, correlation between them
and total SO2 are high.

There is a very strong correlation (0.96) between bound and total sulfur
dioxides. I think that it is why scatterplots for free SO2 vs total SO2 and free
SO2 vs bound SO2 looks very similar.

Correlation between free and bound sulfur dioxide is not so high as expected.
Of course, there are a lot of factors affect to what amount of free SO2 will
bind.

I wish I had more properties, for example age, so I could analyze how
amount of free and bound SO2 depends on wine age.  


#### pH and density

```{r echo=FALSE}
scatterplot_chart(redwine$pH, 
                  redwine$density, 
                  'pH', 
                  'density',
                  'pH and density')
```

This scatterplot looks very interesting. pH and density of wines from dataset
are very concentrated in one sector: where pH is from 3.2 to 3.4 and density is
between 0.994 and 0.9975. 

Correlation between pH and density are negative and equals -0.34.


#### Acids

```{r echo=FALSE}
p1 <- scatterplot_chart(redwine$fixed.acidity, 
                  redwine$volatile.acidity, 
                  'fixed acidity', 
                  'volatile acidity')
p2 <- scatterplot_chart(redwine$fixed.acidity, 
                  redwine$citric.acid, 
                  'fixed acidity', 
                  'citric acid') 
p3 <- scatterplot_chart(redwine$citric.acid, 
                  redwine$volatile.acidity, 
                  'citric acid', 
                  'volatile acidity')
grid.arrange(p1, p2, p3, ncol = 3, top = 'Wine acids')
```

Fixed acidity and citric acid have strong positive correlation. It's expected
since citric acid is a component of tartaric acid. Fixed and volatile acidities,
citric acid and volatile acidity have a negative correlation. First pair of
acids has a weaker connection than other.


# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?
After investigation pairs plot I found 4 variables that affects quality of wine
most:  
* Alcohol: wine with more alcohol have better quality  
* Volatile acidity: better quality wines contain less of it. Probably because
too high level of it can lead to an unpleasant, vinegar taste.  
* Sulphates  
* Citric acid

Both sulphates and citric acid contains in bigger quantities in good wines. Both
correlations is not strong, almost weak. However I don't think that this 4
variables describes quality of wine so well, because of lack of strong
correlations with quality.


### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?
Interesting for me was relationship between volatile acidity and pH. While acids
should have negative correlation coefficient with pH, this acid have it
positive. 

Correlation between bound and total sulfur dioxide is twice stronger
than relationship between free and total SO2.


### What was the strongest relationship you found?
The strongest relationship I found was relationship between bound and total
sulfur dioxides (0.95). Beside this relationship other strong relationship was
fixed acidity and pH (-0.68). But relative to quality of wine strongest
relationship was with alcohol (0.48)


# Multivariate Plots Section

Let's see how alcohol and volatile acidity plots against each other and facet by quality.

```{r echo = FALSE, Multivariate_Plots}
ggplot(data = redwine, aes(x = volatile.acidity, y = alcohol)) +
  facet_wrap(~quality) +
  geom_point(alpha = 0.5, size = 1, position = 'jitter') + 
  ggtitle('Acohol and volatile acidity by quality')
```

There is a difference between points position on quality above 6 and over. With
higher quality positions being more assembled on the left side of scatterplot,
which means less volatile acidity, and stretching higher (more alcohol).
Wines with quality of 7 and 8 have volatile acidity between 0.2 and 0.6 and alcohol level from 10 and over.
While poor quality wines have acidity from 0.4 and above, while alcohol are mostly lower than 11.

```{r echo=FALSE}

color_chart(log10(redwine$sulphates), 
            redwine$alcohol,
            'log10(sulphates)',
            'alcohol',
            'Sulphates and alcohol by rating')
```

This scatterplot confirms that wines with better quality contains more alcohol
and more sulphates.

```{r echo=FALSE}

color_chart(redwine$citric.acid, 
            redwine$volatile.acidity,
            'citric acid',
            'volatile acidity',
            'Citric acid and volatile acidity by rating')

```

It's clearly that good wines (with rating of 7 and 8) have lower volatile acidity
level most values are lower than 0.6. Citric acids values for poor and good
wines are both spread, but it seems that with higher rating amount of citric
acids increases.

```{r echo=FALSE}

color_chart(redwine$fixed.acidity, 
            redwine$pH,
            'fixed acidity',
            'pH',
            'fixed acidity and pH by rating')

```

None of pH or fixed acidity has strong correlation with quality. And it can be
proved by this plot. Wines with different rating are mixed up and it difficult
to find tendency.

```{r echo=FALSE}
color_chart(redwine$free.sulfur.dioxide, 
            redwine$bound.sulfur.dioxide,
            'free sulfur dioxide',
            'bound sulfur dioxide',
            'free and bound sulfur dioxide by rating')
```

Wines with different qualities have3 almost the same range of free SO2.
Most wines with both poor and good (7 and 8 value of quality) have low values of
bound SO2. Wine with average quality have higher bound sulfur dioxide.


### Linear model
```{r echo=FALSE}
m1 <- lm(I(quality) ~ I(alcohol), data = redwine)
m2 <- update(m1, ~ . + volatile.acidity)
m3 <- update(m2, ~ . + sulphates)
m4 <- update(m3, ~ . + citric.acid)
mtable(m1, m2, m3, m4, sdigits = 3)
```

Based on the R-squared value, 4 selected variables explains about 33.6 percent
of the variance in quality. It's not much. And like I see here, citric acid
don't affect results.


# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

After investigating multivariate plots I can make a conclusion about 
some combinations that give high wine quality:  
* Low volatile acidity and high alcohol level  
* High sulphate and alcohol rate  
* Low volatile acidity and high citric acid  
* Low bound sulfur dioxide


### Were there any interesting or surprising interactions between features?
It was interesting to see multivariate plot of free and bound SO2. Most wines 
with poor and high rating had almost same bound SO2 level. There were also 2
outliers that had very high, compared to others, bound SO2 rate (about 250
mg/dm³). Interesting thing was that both wines had same free SO2 value (37.5
mg/dm³ ) and good rating (7 or 8 in quality).


### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

I calculated a linear model, but it shows that those 4 wine attributes that were
correlated most with wine quality explains just 33.6% of variability in quality.
In addition to that, last attribute, which is citric acid were statistically
insignificant.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}

ggplot(aes(x=quality), data=redwine) + 
  scale_x_continuous(limits = c(0, 10), breaks = seq(1, 10, 1)) +
  geom_histogram(binwidth=0.5, fill = I('#7F1734')) + 
  ggtitle('Quality histogram')

```

```{r echo = FALSE}

round(table(redwine$quality)/nrow(redwine), digits = 2)

```

### Description One

Experts graded the wine quality between 0 (very bad) and 10 (very excellent). 
But no wine in dataset have got worst or best grades. Minimum grade is 3 and 
maximum is 8. 83% of wines have wine quality of 5 or 6. While wine with better
quality only 13% and with worse only 4%. It can make it difficult to analyze
wines. If quality dataset have had more uniform distribution it could give a
stronger comparison between good and bad wines.


### Plot Two
```{r echo=FALSE, Plot_Two}

quality_box_chart(redwine$alcohol, 'alcohol')

```

### Description Two

Red wine quality have strongest correlation with alcohol and it equals 0.48. This
boxplot shows that quality of wine increases same as amount of alcohol
increases. So next time you will buy a bottle of red wine, take one with higher
alcohol %.


### Plot Three
```{r echo=FALSE, Plot_Three}

ggplot(data = redwine, aes(x = volatile.acidity, y = alcohol)) +
  facet_wrap(~quality) +
  geom_point(alpha = 0.5, size = 1, position = 'jitter') + 
  ggtitle('Acohol and volatile acidity by quality')

```

### Description Three

Red wine quality affects most by alcohol and volatile acidity. Here I facet it
by wine quality. High alcohol amount and low volatile acidity provides better
wines.

------

# Reflection

I don't drink alcohol, so I though this analysis can help me to get learn 
something about wines and expand my knowledge area.  
I was excited to start analysis and find about which one (or may be more)
attributes affects wine quality.

Dataset I analyzed contains 1599 wine samples with 12 attributes. One of them is
quality, graded by experts. I started with univariate analysis (analysis of each
attribute) using histogram plots, looking to distributions. I met a little
difficulty because I knew nothing about wines, so I spend a lot of time on this
stage, reading articles about wines characteristics and finding information
about each attributes, like what values are normal and how high values of
attributes affects taste of wine. 

After that I started a bivariate analysis. Pairs plot helped me to see all
correlations between variables. I used it as basis for the rest of analysis. I
used box plots and scatterplots to see how 2 variables are related to each
other. Of course I was focused more on relations with wine quality. But when I
analyzed other variables I felt that I'm missing some chemistry knowledge to
understand why variables are correlated.
This stage helped me to get closer to the answer of main question. 

Next step was multivariate analysis, it clarified my findings by use of colored
scatterplots. On this stage I also calculated a linear model for 4 most
correlated to quality attributes.

After analyzing red wine dataset, I came up with following results:  
* None of wines have very poor (1,2) or excellent (9,10) quality. 83% of wines 
have quality of 5 and 6. This can make it harder to determine what makes good
wine vs. bad wine.  
* 4 most correlated to quality attributes are: alcohol, volatile acidity,
sulphates and citric acid.   
  Strongest correlation is with alcohol and equals 0.48.
* Red wines with higher quality have mostly higher alcohol level, less
volatile acidity, more sulphates and more citric acid  
* Fixed acidity has several strong correlations in dataset. It positively
correlated to citric acids and density (coef 0.67) and negatively with pH
(-0.68)  
* Bound sulfur dioxide has correlation coefficient equals to 0.95 with total 
sulfur dioxide. Total SO2 = Free SO2 + Bound SO2. Wines with qualities of 2,3,7 
and 8 have very low bound SO2 amount.  
* Created linear model covered just 33,6% of the variability in quality, which I
think is very low. I wouldn't use this model to predict wine quality.

Highest correlation with quality I've got was 0.48 and I am not satisfied with a
linear model I've got. There was one more difficulty I met between this stage
and nest stage is trying to understand what wine "quality" means. What criteria
experts have used during wine grading? Was is just taste score or not? Also, I
really wish I could have more attributes to analyze, like wine age, price,
region, grape type. All these could help to build more precise linear model,
which I could use to determine what bottle of red wine, I've got some present, I
should keep to myself and what I can give away;)




